Informing policy via dynamic models: Eliminating cholera in Haiti

### 2022-12-05 ms.Rnw
Fixed model3 fitting rs.sd typo

set_rw_1 <- function(x) {
  if (gsub("[[:digit:]]+$", "", x) %in% shared_param_names) {
    return(0.01)
  } else if (x %in% paste0(rep(c("aHur", 'hHur'), each = 2), c(3, 9))) {
    return(expression(ifelse(time >= 2016.754 & time <= 2017, 0.015, 0)))
  } else if (x %in% c("Iinit3", "Iinit7", "Iinit10")) {
    return(expression(ivp(0.25)))
  } else if (grepl('^foi_add[[:digit:]]+$', x)) {
    return(0.015)
  } else {
    return(0)
  }
}

set_rw_2 <- function(x) {
  if (gsub("[[:digit:]]+$", "", x) %in% shared_param_names) {
    return(0.003)
  } else if (x %in% paste0(rep(c("aHur", 'hHur'), each = 2), c(3, 9))) {
    return(expression(ifelse(time >= 2016.754 & time <= 2017, 0.005, 0)))
  } else if (x %in% c("Iinit3", "Iinit7", "Iinit10")) {
    return(expression(ivp(0.125)))
  } else if (grepl('^foi_add[[:digit:]]+$', x)) {
    return(0.005)
  } else {
    return(0)
  }
}

set_rw_3 <- function(x) {
  if (gsub("[[:digit:]]+$", "", x) %in% shared_param_names) {
    return(0.0025)
  } else if (x %in% paste0(rep(c("aHur", 'hHur'), each = 2), c(3, 9))) {
    return(expression(ifelse(time >= 2016.754 & time <= 2017, 0.005, 0)))
  } else if (x %in% c("Iinit3", "Iinit7", "Iinit10")) {
    return(expression(ivp(0.125)))
  } else if (grepl('^foi_add[[:digit:]]+$', x)) {
    return(0.003)
  } else {
    return(0)
  }
}

>>>>

set_rw_1 <- function(x) {
  if (gsub("[[:digit:]]+$", "", x) %in% shared_param_names) {
    return(0.01)
  } else if (x %in% paste0(rep(c("aHur", 'hHur'), each = 2), c(3, 9))) {
    return(expression(ifelse(time >= 2016.754 & time <= 2017, 0.015, 0)))
  } else if (x %in% c("Iinit3", "Iinit7", "Iinit10")) {
    return(expression(ivp(0.25)))
  } else if (grepl('^foi_add[[:digit:]]+$', x)) {
    return(0.015)
  } else if (grepl('^betaB[[:digit:]]+$', x)) {
    return(0.01)
  } else {
    return(0)
  }
}

set_rw_2 <- function(x) {
  if (gsub("[[:digit:]]+$", "", x) %in% shared_param_names) {
    return(0.003)
  } else if (x %in% paste0(rep(c("aHur", 'hHur'), each = 2), c(3, 9))) {
    return(expression(ifelse(time >= 2016.754 & time <= 2017, 0.005, 0)))
  } else if (x %in% c("Iinit3", "Iinit7", "Iinit10")) {
    return(expression(ivp(0.125)))
  } else if (grepl('^foi_add[[:digit:]]+$', x)) {
    return(0.005)
  } else if (grepl('^betaB[[:digit:]]+$', x)) {
    return(0.003)
  } else {
    return(0)
  }
}

set_rw_3 <- function(x) {
  if (gsub("[[:digit:]]+$", "", x) %in% shared_param_names) {
    return(0.0025)
  } else if (x %in% paste0(rep(c("aHur", 'hHur'), each = 2), c(3, 9))) {
    return(expression(ifelse(time >= 2016.754 & time <= 2017, 0.005, 0)))
  } else if (x %in% c("Iinit3", "Iinit7", "Iinit10")) {
    return(expression(ivp(0.125)))
  } else if (grepl('^foi_add[[:digit:]]+$', x)) {
    return(0.003)
  } else if (grepl('^betaB[[:digit:]]+$', x)) {
    return(0.0025)
  } else {
    return(0)
  }
}
